---
title: "filelist"
output:
  html_document:
    df_print: paged
---
```{r}
## whether HOST is set will be shell-dependent e.g. Solaris' csh does not.
Sys.getenv(c("HOME"))

names(s <- Sys.getenv()) # all settings (the values could be very long)
head(s, 12)# using the Dlist print() method

## Language and Locale settings -- but rather use Sys.getlocale()
s[grep("^L(ANG)", names(s))]
```


```{r}
fn <- list.files(path = ".", pattern = "*R*", all.files = FALSE,
           full.names = TRUE, recursive = FALSE,
           ignore.case = TRUE, include.dirs = TRUE, no.. = FALSE)

View(fn)
print(pwd())
```


```{r}
dir()
```

```{r}
ls
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

